---
title: "Warlpiri dictionary test suite"
date: "Generated `r format(Sys.time(), '%H:%M, %d %B, %Y')`"
output: 
  html_document: 
    toc: yes
params:
   lexicon_path: "~/git-repos/coedl/warlpiri-2018/src/wlp-lexicon_master.txt"
   CI_ENV: false
---

```{r setup, include=FALSE}
library(yinarlingi)
library(purrr)
library(knitr)

# Set global knitr options
opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

# Helper functions for pretty printing
escape_md <- . %>%
    str_replace_all("\\\\", "\\\\\\\\") %>% 
    str_replace_all("\\^", "\\\\^") %>%
    str_replace_all("\\*", "\\\\*")

kable_escaped <- . %>%
    mutate_if(is.character, funs(escape_md)) %>%
    kable()

prettify_data_col <- . %>%
    mutate(data = str_trunc(data, width = 50, ellipsis = "\t..."))

# Read in data

skeleton_grammar <-
    system.file("structures/wlp_skeleton-simple.ne", package = "yinarlingi") %>%
    readLines()

wlp_code_defs <-
    readr::read_csv(
        file      = system.file("structures/wlp_code-definitions.csv", package = "yinarlingi"),
        col_types = "ccc"
    )

wlp_df <-
    read_wlp_lexicon(params$lexicon_path)

test_df <-
    skeletonise_df(wlp_df)

# Coverage = lines in skeleton / lines in raw data
cov_pc <-
    `/`(
        test_df %>% nrow(),
        wlp_df %>% filter(!is.na(code1)) %>% nrow()
    ) %>%
    `*`(100) %>%
    round(digits = 2)

strays_df <-
    wlp_df %>%
    filter(!is.na(code1), !code1 %in% wlp_code_defs$code1)

test_results <-
    list(
        "syntax_ok"  = . %>% test_code1_ordered %>% group_by(me_start) %>% tidyr::nest(),
        "inline_ok"  = . %>% test_inline_codes_ok %>% ungroup %>% prettify_data_col,
        "xrefs_ok"   = . %>% test_xrefs_homed %>% prettify_data_col
    ) %>%
    map(~ .(test_df))

test_status <-
    test_results %>%
    map(~ ifelse(nrow(.) == 0, "passing", "failing"))

```

<span class="badge tag">tests</span>`r ifelse(all(test_status == "passing"), '<span class="badge value build-passing">passing</span>', '<span class="badge value build-failing">failing</span>')`

# About

To do

## Defined codes

```{r Show codes}
kable(wlp_code_defs)
```


## Skeleton grammar

```{r Show grammar, comment=''}
cat(skeleton_grammar, sep = '\n')
```


# Diagnostics

## Coverage (`r cov_pc`%)

```{r Show coverage statistics}
residual_codes <-
    wlp_df %>%
    filter(!code1 %in% unique(test_df$code1)) %>%
    pull(code1) %>%
    unique() %>%
    sort()

```

The current skeleton grammar covers `r cov_pc`% of the raw dictionary data. The residual codes current unprocessed are:
`r residual_codes`

# Within-line tests

The tests within this section operate on individual lines

## Test that there are no stray codes (`r ifelse(nrow(strays_df) == 0, "passing", "failing")`)

**Common issues**:

Valid end codes (e.g. `edm`, `ewe`) appear in the strays list. These codes appear as stray because they technically are not valid as `code1` codes, i.e. the first code from the left-edge of the line. They should be placed as a 2nd, ending code to a previous line, e.g. (note that `dm` is the left-most code, not `edm`):
    <pre>\dm ... (\edm should go here)
<b>\edm</b></pre>


```{r Show stray codes}
kable_escaped(strays_df)
```


`ewe` appears as a left-most code, thus considered 'stray'. Note that the end example codes, `ewe` or `ewe` should appear on the English translation line, i.e. `\et ... \ewe` or `\et ... \ewed`

## Test that only expected backslash codes appear in each line (`r test_status$inline_ok`)

Description of test here

```{r Show inline codes validity results}
kable_escaped(test_results$inline_ok)
```

## Test that there are no orphaned cross-references (`r test_status$xrefs_ok`)

```{r Show orphaned cross-references}
kable_escaped(test_results$xrefs_ok)
```

# Between-line tests

These tests 

## Test that code sequence within an entry follows expected structure (`r test_status$syntax_ok`)

```{r Show current grammar, comment=''}
cat(skeleton_grammar, sep = '\n')
```


```{r Show code ordering validity results}
test_results$syntax_ok %>%
    mutate(failing_line = map_int(data, ~ filter(., code1_ok == FALSE) %>% pull(line))) %>%
    unnest(data,.drop = FALSE) %>%
    filter(line >= failing_line - 3, line <= failing_line + 3) %>%
    ungroup %>%
    mutate(me_start = ifelse(duplicated(me_start), "", me_start)) %>%
    prettify_data_col %>% 
    select(-failing_line) %>%
    kable_escaped()

```


<style type="text/css">
h1 { font-size: 1.2em }
h2 { font-size: 1.1em }
.badge {
    font-family: DejaVu Sans, Verdana, Geneva, sans-serif;
    font-size: 11px;
    color: white;
}

.badge.tag {
    background-color: #4c4c4c;
    padding: 2px 4px 3px 7px;
    border-radius: 4px 0 0 4px;
}

.badge.value {
    padding: 2px 7px 3px 4px;
    border-radius: 0 4px 4px 0;
}

.badge.license {
    background-color: #487;
}

.badge.build-passing {
    background-color: #4b2;
}

.badge.build-failing {
    background-color: #c54;
}
</style>
